Expression QTL hotspot dissection with mediation analysis and pleiotropy testing

### 2019-07-24 analysis/paper/paper.Rnw
fixed package name in paper.Rnw

<<setup>>=
library(hotspots)
pleio_threshold <- 4
ult <- 15 # univariate lod threshold
@

@@

<<make_pm-2>>=
pm <- pleio_tib %>%
  hotspots::tibble_to_matrix(symmetric = TRUE)
@

@@

pm[ord, ord] %>%
  apply(FUN = hotspots::trunc2, MARGIN = 2, threshold = 5) %>%
  heatmaply(Rowv = FALSE,
            Colv = FALSE,
            cexRow = 0.2,
            cexCol = 0.2,
            symm = TRUE,
            row_side_colors = scols[ord, ],
            col_side_colors = scols1[ord],
            limits = c(0, 5)
            )
@

>>>>

<<setup>>=
library(qtl2hotspots)
pleio_threshold <- 4
ult <- 15 # univariate lod threshold
@

@@

<<make_pm-2>>=
pm <- pleio_tib %>%
  tibble_to_matrix(symmetric = TRUE)
@

@@

pm[ord, ord] %>%
  apply(FUN = trunc2, MARGIN = 2, threshold = 5) %>%
  heatmaply(Rowv = FALSE,
            Colv = FALSE,
            cexRow = 0.2,
            cexCol = 0.2,
            symm = TRUE,
            row_side_colors = scols[ord, ],
            col_side_colors = scols1[ord],
            limits = c(0, 5)
            )
@
